Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-29 paper/paper.tex
cite pearce 2019

The European symphonic orchestra encompasses four families of instruments: strings, woodwinds, brass, and percussion.
In this article, we focus on the former three, and leave the question of learning auditory similarities between percussion instruments to future research.
The reason behind this choice is that most percussive instruments do not allow much variation in terms of pitch or intensity, if at all; thus reducing the amount of intra-technique variability in the time--frequency domain.
Furthermore, although percussive instruments certainly exhibit a rich diversity of playing techniques (we refer to \cite{peinkofer1976book} for a survey) these are rarely shared with pitched instruments.
In comparison, techniques for sustained tones such as \emph{vibrato} or \emph{tremolo} permeate throughout a vast instrumentarium, \eg{} bowed strings and reed alike.
We refer to \cite{wu2018taslp} and \cite{x} for reviews of the recent literature on the timbre modeling of percussive instruments, from the standpoints of MIR and music cognition respectively. % TODO VL CITE

>>>>

The European symphonic orchestra encompasses four families of instruments: strings, woodwinds, brass, and percussion.
In this article, we focus on the former three, and leave the question of learning auditory similarities between percussion instruments to future research.
The reason behind this choice is that most percussive instruments do not allow much variation in terms of pitch or intensity, if at all; thus reducing the amount of intra-technique variability in the time--frequency domain.
Furthermore, although percussive instruments certainly exhibit a rich diversity of playing techniques (we refer to \cite{peinkofer1976book} for a survey) these are rarely shared with pitched instruments.
In comparison, techniques for sustained tones such as \emph{vibrato} or \emph{tremolo} permeate throughout a vast instrumentarium, \eg{} bowed strings and reed alike.
We refer to \cite{wu2018taslp} and \cite{pearce2019appliedsciences} for reviews of the recent literature on the timbre modeling of percussive instruments, from the standpoints of MIR and music cognition respectively. % TODO VL CITE
